\documentclass[]{article}
\usepackage{graphicx}

\parindent=0pt
\usepackage[margin=0.5in]{geometry}

\begin{document}
\pagestyle{empty}
{\large\textbf{Research Notes}}
\begin{itemize}
    \item[*] Created on Sept 29, 2014
    \item[*] Modified on \today
    \item[*] Author info: Boyou Zhou\\
             8 St Mary's St, PHO 340, Boston, MA 02215\\
             Email: bobzhou@bu.edu, Phone: 617-678-8480
\end{itemize}


\rule[-0.1cm]{7.5in}{0.01cm}\\
\\
\noindent \textbf{Sept 29,2014}
\textit{proceedings on hardware security}
\indent		\begin{itemize}

            \item \textit{State-of-art defenses} 
                \begin{itemize}

                    \item \textit{invasive} precies measurement throughout all the gates, in order to check
                    how the gates are arranged. It is too expensive for small companies.

                    \item \textit{non-invasive} External parametric and functional IC testing. Such corresponding
                    metrics are delay, quiescent leakage, and dynamic leakage.
                    Example testing includes transient power analysis, path-delay meausurements, gate level
                    characterization, thermal profiling, or combination.

                \end{itemize}
        \end{itemize}

\noindent \textbf{Sept 30,2014}
\textit{Low Power Memristor-based ReRAM Design with Error Correcting Code }
\indent		\begin{itemize}
            \item \textit{before everything} I feel very confused is that people do not care about ecc in the 
            digital calculation circuits. I tried to find out how people have done similar work, but the result
            is none.
            \item \textit{main motivation} There are traditional error correcting code for the conventional design
            of DRAM. The author has proposed the idea to use the ECC for the memristor.
            The main idea is to use the ecc for the memristor-based memory. The author check how many bits for ecc
            is the most energy efficiency.

            \item \textit{critics} Not very innovative, it's just move all the schemes in the traditional design 
            into the memristor scheme.
        \end{itemize}
\end{document}

